\roleheader
{Amazon Web Services, Inc.}
{Seattle, Washington}
{Cloud Support Engineer \RNum{2}}
{2016-10-01}
{2018-09-17}

\begin{itemize}
    \item Functioned as a technical leader within the support organization, serving as the final escalation point for critical issues and mentoring peers to elevate team capabilities.
    \item Presented at the ECS Global Subject Matter Expert Summit to an audience of solution architects, product leadership, and premium support.
    \item Served as the primary Point of Contact for ECS, ECR, Fargate, EKS, and Docker, providing support to service teams, solution architects, and leadership.
    \item Served as the preferred engineer and single point of contact for all ECS, ECR, and Docker matters for a large customer, contributing to the successful launch of a feature used by up to 100 million daily users.
    \item Traveled to Berlin to deliver a presentation on ECS and Prometheus monitoring to a fast-growing startup.
    \item Designed and implemented new support processes and internal tooling, streamlining workflows and enhancing the feedback loop between support and engineering teams.
    \item Played a pivotal role in the launch of Amazon Fargate and Amazon Elastic Kubernetes Service by:
          \begin{itemize}
              \item Creating and delivering training materials for premium support on the new services.
              \item Collaborating with the service team to advocate for customer features.
              \item Educating the service team about the premium support experience and how they can best serve premium support.
          \end{itemize}
\end{itemize}