\roleheader
{Google, Inc.}
{Asheville, North Carolina}
{Technical Account Manager for Alphabet, Google Cloud Professional Services}
{2021-08-09}
{}
\begin{itemize}

    \item Led a 4-month workstream that resulted in over \$XX million in cost savings for Alphabet, which included:
          \begin{itemize}

              \item Created email templates and managed customer issue tickets with a 2-day SLA on updates.

              \item Provided leadership with weekly email reports and a real-time spreadsheet to track the end-to-end status of each item, including contact methods and customer progress.

              \item Automated the creation of tickets from emails to ensure accountability and visibility, centralizing all communications to prevent sprawling threads.

              \item Collaborated closely with a Cloud Billing Manager and Program Manager (PgM) through bi-weekly check-ins to ensure the workstream progressed on schedule and met the 4-month deadline.

          \end{itemize}

    \item Spearheaded support for Google's internal data lake, acting as a Program Manager for all end-user-facing aspects, driving initiatives to enhance the user experience and reduce support friction. This workstream also included:

          \begin{itemize}

              \item Ensuring seamless, top-notch operations to enable data-driven decision-making.

              \item Collaborating with cross-functional teams to develop and maintain an internal Knowledge Base (KB) for the data lake, which included:
              \begin{itemize}
                    \item Getting started guides (basic and advanced)
                    \item Six troubleshooting playbooks
                    \item Escalation paths for the end-user to reach the engineering teams
              \end{itemize}

              \item Writing and updating policies in response to new data lake features, changes within Alphabet (e.g., layoffs, shifting development focuses), and other organizational shifts.

          \end{itemize}

    \item Collaborated closely with the NVIDIA team supporting Alphabet's internal GPU usage to foster strong relationships and drive key initiatives, including:

          \begin{itemize}

              \item Partnering with NVIDIA and the Confidential Computing Product Manager (PM) to deliver a recorded training session to my team.

              \item Creating self-service training for Alphabet employees on GPU procurement methods, including information on how to contact NVIDIA for support.

          \end{itemize}

    \item Mentored two new team members by conducting regular check-ins to support their professional development and rapid onboarding, fostering an environment where they felt empowered to ask questions without fear of judgment.

    \item Managed strategic partnerships with key stakeholders as the Technical Account Manager for two of Google's leading AI departments.

\end{itemize}