\roleheader
    {Amazon Web Services, Inc.}
    {Seattle, Washington}
    {Cloud Support Engineer \RNum{2}}
    {2016-10-01}
    {2018-09-17}
\begin{itemize}

    \item Served as the highest tier of support, mitigating escalations to the respective service team and improving turnaround time on customer issues.

    \item Presented at the ECS Global Subject Matter Expert Summit to an audience of solution architects, product leadership, and premium support.

    \item Acted as the Point of Contact for ECS, ECR, Fargate, EKS, and Docker, providing support to service teams, solution architects, and leadership.

    \item Served as the preferred engineer and single point of contact for all ECS, ECR, and Docker matters for a large customer, contributing to the successful launch of a feature used by up to 100 million daily users.

    \item Traveled to Berlin to deliver a presentation on ECS and Prometheus monitoring to a fast-growing startup.

    \item Improved processes within the support organization by:
    \begin{itemize}
        \item Strengthening the relationship with the documentation team to reduce customer contacts and clarify complex topics.
        \item Leading a project to create and update internal tooling for premium support.
    \end{itemize}

    \item Contributed to the launch of Amazon Fargate and Amazon Elastic Kubernetes Service by:
    \begin{itemize}
        \item Creating and delivering training materials for premium support on the new services.
        \item Collaborating with the service team to advocate for customer features.
        \item Educating the service team about the premium support experience and how they can best serve premium support.
    \end{itemize}

\end{itemize}