\roleheader
    {Amazon Web Services, Inc.}
    {Seattle, Washington}
    {Cloud Support Engineer \RNum{1}}
    {2015-04-13}
    {2016-10-01}
\begin{itemize}

    \item Represented AWS at DockerCon 2016 in Seattle as the sole AWS Premium Support Engineer, engaging in one-on-one interactions with customers to understand their needs and gather feedback on ECS and AWS.

    \item Provided best practices and conducted troubleshooting for high-severity issues for AWS customers using deployment management services such as Elastic Beanstalk, EC2 Container Service (ECS), EC2 Container Registry (ECR), CloudFormation, OpsWorks, CodeDeploy, CodePipeline, and CodeCommit.

    \item As one of three premium support engineers, met bi-weekly with ECS/ECR product leadership to advocate for customers by:
    \begin{itemize}
        \item Highlighting feature requests and bug reports.
        \item Addressing customer complaints.
        \item Improving inter-team communication.
    \end{itemize}

    \item Collaborated with the AWS Premium Support office in Sydney, Australia to create comprehensive training materials for ECS, ECR, and Docker, covering introductory, intermediate, advanced, and Subject Matter Expert (SME) levels.

    \item Became an accredited ECS Subject Matter Expert (SME), a distinction validated and approved by the creators of Amazon Elastic Container Service.

    \item Participated in "Ask an Architect" at the AWS Pop-up Loft in San Francisco, providing 60-minute one-on-one sessions to attendees on topics such as:
    \begin{itemize}
        \item Technical deep dives into AWS and Docker.
        \item Fundamentals of cloud computing and DevOps.
    \end{itemize}

    \item Attended the ECS Global Subject Matter Expert Summit to represent the needs of customers and support teams to solution architects and product leadership.

\end{itemize}