\roleheader
    {Amazon Web Services, Inc.}
    {San Antonio, Texas}
    {Specialist Technical Account Manager for Container Technologies}
    {2018-09-17}
    {2021-07-06}
\begin{itemize}

    \item As the first Specialist Technical Account Manager (STAM) for Containers at AWS, helped shape the role and direction of the STAM organization.

    \item Provided guidance to enterprise AWS customers on building highly scalable, flexible, and resilient cloud workloads, leveraging a broad range of technologies and skills.

    \item Acted as a technical liaison between customers, service teams, and support, ensuring the customer's voice was heard during:
    \begin{itemize}
        \item Product creation.
        \item Escalations.
        \item Product improvements.
    \end{itemize}

    \item Developed a proof-of-concept monitoring infrastructure that monitored 1.5 million vCPUs and over 55,000 Amazon EC2 servers with a 1-minute monitoring SLA. The setup included:
    \begin{itemize}
        \item Prometheus for metric collection and storage.
        \item Grafana for custom dashboards.
        \item Docker for deployment.
        \item Amazon EC2 for servers.
        \item Amazon Application Load Balancer for load balancing requests to Grafana.
        \item Prometheus Node Exporter for server-level metrics.
    \end{itemize}

    \item Collaborated with a Fortune 500 customer's engineering team to resolve a production outage, leading to the identification of a software bug that could have impacted other customers.

    \item Co-developed the "EKS Log Collector," now included in the Amazon Elastic Kubernetes Service AMI and GitHub repository, which helped decrease case resolution time and reduce the total number of correspondences.

\end{itemize}